Survival Compass: Statistical Insights into Lung Cancer Patients' Journey Post-Diagnosis

### 2024-04-01 paper/paper.qmd
Edited author, code and added an abstract. Added llm for abstract.

---
title: "From Theory to Practice: Investigating Treatment Responses in Breast Cancer"
subtitle: "My subtitle if needed"
author: 
  - First author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

>>>>

---
title: "Survival Compass: Statistical Insights into Lung Cancer Patients' Journey Post-Diagnosis"
author: 
  - Lexi Knight
thanks: "Code and data are available at: https://github.com/LexiKnight/Lung_Cancer/tree/main"
date: today
date-format: long
abstract: "This study investigates the impact of pathogenic stage and treatment modalities on lung cancer survival post-diagnosis. Analysis of patient data reveals significant correlation between pathogenic stage, seeking treatment and survival outcomes. Notably, patients at advanced stages with metastases in distant sites beyond the lung, extensive lymph node involvement and tumors with extensive growth, invading nearby structures demonstrate lower survival rates. These findings underscore the critical importance of early detection, tailored treatment strategies and ongoing research efforts to enhance lung cancer survival rates globally."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# install packages
install.packages("knitr")
install.packages("kableExtra")

# load packages
library(tidyverse)
library(knitr)
library(kableExtra)
